Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-15 MDPI_submission.tex
Commit 2023-12-15 13:08

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & Rsqrd & Pearson cor. & Sky conditions & Days & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5 & mean\_clima & ChangeWpY\\
\midrule
0.376 & 0.00830 & 0.0911 & All skies & 10250 & 4.727 & 1.96 & 0.000811 & 0.001246 & 387 & 1.45\\
0.097 & 0.01908 & 0.1381 & Clear skies & 2689 & 0.476 & 1.96 & 0.000194 & 0.000338 & 515 & 0.50\\
0.408 & 0.00657 & 0.0810 & Cloudy skies & 4937 & 3.566 & 1.96 & 0.000733 & 0.001499 & 290 & 1.18\\
\bottomrule
\end{tabu}
\end{table}

>>>>

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & Rsqrd & Pearson cor. & Sky conditions & Days & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5 & mean\_clima & ChangeWpY\\
\midrule
0.3756 & 0.00830 & 0.0911 & All skies & 10250 & 4.727 & 1.96 & 0.000811 & 0.001246 & 387 & 1.452\\
0.0972 & 0.01912 & 0.1383 & Clear skies & 2684 & 0.476 & 1.96 & 0.000194 & 0.000338 & 515 & 0.501\\
0.4077 & 0.00657 & 0.0810 & Cloudy skies & 4937 & 3.566 & 1.96 & 0.000733 & 0.001499 & 290 & 1.181\\
\bottomrule
\end{tabu}
\end{table}
